\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

\hspace{3ex}
First of all, we would like to express our heart-felt indebtness to our supervisor Dr. \hspace{-0.8ex}Tanzima Hashem for introducing us to the intriguing subject of spatial alarms, guiding us through the path of conducting successful research and above all for always being supportive and kind as a real mentor should be. She corrected our error with infinite patience and sought to make our research work perfect by giving us valuable advice. Her suggestions drove us towards better ways of thinking, her reviews enriched us in solving research problems, and her support gave us strength at the time of our disappointment and failures. It was our greatest pleasure and good fortune to work with her. We will always remember this enlightening experience. 

We would like to sincerely thank Nusrat Sultana Shetu for her guidance and encouragement in developing our thesis work. Her insights have greatly helped us in finishing our experiments.During the thesis work evaluation process, the teachers of our department made valuable comments which helped us a lot in refining our work. We express our gratitude to them all.

We are indebted to Md. Shahin Pramanik, a member of the Samsung Innovation Laboratory, who provided us with a congenial research environment in the lab while we were conducting our work there.

Last but not the least, we deeply thank our friends and families for always believing in us even at the moment when we were losing our believes in ourselves. We are forever grateful to them for their selfless support and understanding.





