
\chapter*{}
%\typeout{Abstract}
\addcontentsline{toc}{chapter}{Declaration}
\vspace{-3cm}
\begin{center}
\vfill

\textbf{\Large {\bf Declaration}}

\vfill
\vfill

{\bf Supervisor's Declaration}
\end{center}
\vfill
\footnotesize{
I confirm that, to the best of my knowledge, the research was carried out and the thesis was prepared under my direct supervision. It represents the original research work of the candidates. The contribution made to the research by me and by other members of staff of the University was consistent with normal supervisory practice. I have read this work and in my opinion this work is adequate in terms of scope and quality for the purpose of awarding the degree of Bachelor of Science in Computer Science and Engineering.
\vfill
\vfill
\vspace{0.6cm}
\flushright{
\rule{40mm}{0.1mm}\\
Tanzima Hashem, PhD\\
Assistant Professor\\
Department of Computer Science and Engineering \\
Bangladesh University of Engineering and Technology (BUET)\\Dhaka-1000.\\
}
}
\vspace{1.0cm}
\normalsize
\begin{center}
{\bf Candidates' Declaration}
\end{center}
\vfill
\footnotesize{
We confirm that, the work presented in this thesis entitled \lq\lq{}{\bf Efficient Computation of Spatial Alarms in the Obstructed Space}\rq\rq{} is the outcome of the investigations carried out by us under the supervision of Assistant Professor Dr. Tanzima Hashem in the Department of Computer Science and Engineering, Bangladesh University of Engineering and Technology (BUET), Dhaka. We also declare that, neither this thesis nor any part thereof has been submitted or is being currently submitted anywhere else for the award of any degree or diploma.
\vspace{1.5cm}
\flushleft{
\begin{multicols}{2}

\rule{40mm}{0.1mm}\\
Md. Touhiduzzaman\\
Student No.: 1005018\\

\rule{40mm}{0.1mm}\\
Sezana Fahmida\\
Student No.: 1005057\\

\vfill

\end{multicols}
}
}
\normalsize
\vfill
\endinput
